% YAAC Another Awesome CV LaTeX Template
%
% This template has been downloaded from:
% https://github.com/darwiin/yaac-another-awesome-cv
%
% Author:
% Christophe Roger
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%Section: Work Experience at the top
\sectionTitle{Work Experience}{\faSuitcase}
%\renewcommand{\labelitemi}{$\bullet$}
\begin{experiences}
  \experience
    {Present}   {Software Engineering Intern (part-time)}{Autodesk}{Bonn, Germany}
    {July 2018} {
                      \begin{itemize}
                        \item Working on developing infrastructure for a cloud based data processing pipeline.
                        \item Creation and extension of backend services, front-end components, and related command line tools.
                        \item Involved with continuous integration of the platform with Jenkins and creation of automated tests.                               
                      \end{itemize}
                    }
                    {JavaScript, Node.Js, DynamoDB, AWS S3, Mocha, Jenkins, VSCode}
  \emptySeparator
  \experience
    {June 2018} {Software Developer (part-time)}{All Things Internet GmbH}{Sankt Augustin, Germany}
    {September 2017}    {
                      \begin{itemize}
                        \item Worked on back-end development for the start-up.
                        \item Developed the database; worked on related routes and functionalities.                   
                      \end{itemize}
                    }
                    {JavaScript, Node.Js, MongoDB, PostgreSQL, VSCode}
  \emptySeparator
  \experience
    {November 2016}     {Software Engineer}{TechMahindra}{Pune, India}
    {November 2014}    {
                      \begin{itemize}
                        \item Worked as a developer for PeopleSoft HRMS applications.
                        \item Was involved in developing solutions for new requirements, root cause analysis and bug fixes, performance improvement and unit testing.
                        \item Was also involved in providing technical support for the relevant applications.
                      \end{itemize}
                    }
                    {Oracle PeopleSoft HRMS, Oracle SQL, PL/SQL, JAVA, JEE}
\end{experiences}
